---
title: "SRT411-Assignment0"
author: "Kaji Vasantharuban"
date: "February 19, 2019"
output:
  pdf_document: default
  html_document: default
---



##3.1 Calculator
###Percentage of your life you have spent at this university.
```{r}
((2019-2017)/(2019-1990))*100
```

##3.2 Workspace
###Percentage of your life you have spent at this university. (Using Varables)
```{r}
curent_year = 2019
born_year = 1998
start_year = 2016
(start_year-curent_year)/(curent_year-born_year)*100
```

##3.4 Functions
###Compute the sum of 4, 5, 8 and 11 by first combining them into a vector and then using the function sum.
```{r}
func = c(4,5,8,11)
sum(func)
```

##3.5 Plots
###Plot 100 normal random numbers.
```{r}
random=rnorm(100)
plot(random)
```

##4 Help and documentation
###Find help for the sqrt function.
```{r}
help(sqrt)
```

##5 Scripts
###Make a file called firstscript.R containing Rcode that generates 100 random numbers and plots them, and run this script several times.
```{r}
source("firstscript.R")
```

##6.2 Matrices
###Put the numbers 31 to 60 in a vector named P and in a matrix with 6 rows and 5 columns named Q. 
```{r}
P = seq(from=31, to=60, by=1)
Q=matrix(P,nrow=6,ncol=5)
Q
```

##6.3 Data frames
###Make a script file which constructs three random normal vectors of length 100.
```{r}
x1=rnorm(100)
x2=rnorm(100)
x3=rnorm(100)
t = data.frame(a=c(x1), b=c(x1+x2), c=c(x1+x2+x3))
plot(t)
sd(t$a)
sd(t$b)
sd(t$c)
```

##7 Graphics
###Script
```{r}
source("secondscript.R")
```

##8 Reading and writing data files
###Make a file called tst1.txt in Notepad from the example in Figure 4 and store it in your working directory. Write a script to read it, to multiply the column called g by 5 and to store it as tst2.txt.
```{r}
source("thirdscript_write.R")
```

##9 Not available data
###Compute the mean of the square root of a vector of 100 random numbers. What happens?
```{r}
vector=rnorm(100)
cal=sqrt(vector)
result= mean(cal)
result
```

##10.2 Dates
###Make a graph with on the x-axis: today, Sinterklaas 2014 and your next birthday and on the y-axis the number of presents you expect on each of these days. Tip: make two vectors first.
```{r}
dates=strptime(c("20190912", "20200912"), format="%Y%m%d")
presents = c(2,1)
plot(dates, presents, type="l", ylim=range(t),lwd=3, col=rgb(1,0,0,0.5))
```

##11.2 For-loop
###Make a vector from 1 to 100. Make a for-loop which runs through the whole vector. Multiply the elements which are smaller than 5 and larger than 90 with 10 and the other elements with 0.1.
```{r}
vector2=seq(1,100)
for(number in vector2)
{
if(number<5|number>90)
{
  vector2[number] = number*10
}else{
  vector2[number] = number*0.1
}
}
vector2
```